Bayesian Rate Estimation

### 2012-08-16 many.tex
Typo in k-loudest events fixed.

\subsubsection{Loudest event statistic}
If we were to include only the $k$-loudest events in the posterior
distribution, rather than all observed events, the posterior
(Eq.~\eqref{eq:posterior}) would be modified by an additional factor
of $\exp[R_f \hat{F}(x_{N-k+1}) + R_b \hat{B}(x_{N-k+1})]$, where we
have assumed events are ordered by loudness, so that $x_{N-k+1}$ is
the $k$-th loudest event. This term accounts for the data-dependent
threshold that a loudest event statistic employs.

>>>>

\subsubsection{Loudest event statistic}
If we were to include only the $k$-loudest events in the posterior
distribution, rather than all observed events, the posterior
(Eq.~\eqref{eq:posterior}) would be modified by an additional factor
of $\exp[R_f \hat{F}(x_{N-k+1}, \theta) + R_b
  \hat{B}(x_{N-k+1},\theta)]$, where we have assumed events are
ordered by loudness, so that $x_{N-k+1}$ is the $k$-th loudest
event. This term accounts for the data-dependent threshold that a
loudest event statistic employs.
